---
title: "Mapping census block groups"
author: "Steve Simon"
date: "Created on 2021-09-22"
output: html_document
---

I will eventually want to move this and other programs to a new github site:

https://gitub.com/sg4cd

and to a private repository (Satya).

```{r prelims}
library(sf)
library(tidyverse)
```

You can find shapefiles for census block groups at
[the U.S. Census website](https://www.census.gov/geographies/mapping-files/time-series/geo/cartographic-boundary.html)

The census files use a shapefile format. This is a rather complex system with at least three separate files constituting the shapefile. You can find a nice introduction at the
[Wikipedia page on shapefiles](https://en.wikipedia.org/wiki/Shapefile).

The st_read function is part of the sf library. It reads a shape file and converts it to an sf object. An sf (simple features object) is a data frame where the last column is a list-column, an sfc object.

The list column represents geographic features either as a single data points (POINT), multiple data points (MULITPOINT), a two-dimensional path (LINESTRING), multiple paths (MULTILINESTRING), a polygon (POLYGON), or multiple polygons (MULTIPOLYGON).

The POLYGON and MULTIPOLYGON features can include holes, and there are complex rules for geographic features with holes.

```{r read}
path_name <- "../data"
list.files(path_name)
```

```{r read-2}
file_name <- "tl_2020_29_tabblock20.shp"
path_name                              %>%
  paste(file_name, sep="/")            %>%
  st_read(stringsAsFactors=FALSE)      -> all_census_blocks
```

The sf object looks and acts like an ordinary data frame. But the last column is quite unusual.

```{r sf}
names(all_census_blocks)
head(all_census_blocks)
```


```{r built-in-tools}
all_census_blocks                          %>%
  filter(COUNTYFP20=="095") %>%
  ggplot()                              +
  geom_sf(aes())                 +
  ggtitle("Test")
```

Save everything for possible later use.

```{r save-everything}
save.image("../data/census-block-example.RData")